On the discovery and origin of $r$-process stars in the Milky Way

### 2018-02-27 article/ms.tex
I got 96 for this subject which is just primo get around me

	\begin{abstract}
		The production of heavy elements occurs through the slow and rapid neutron capture process. Numerous sites satisfy the conditions needed for the r-process but the relative frequency of these sites is unknown, largely due to the lack of a large number of stars with strong r-process signatures. Here we report the discovery of 47 r-process enhanced stars discovered in the second LAMOST data release (DR2), more than doubling the known number in the Galaxy. Taking expected rates of core-collapse supernovae and the average r-process material ejected per event, we find that core-collapse supernovae alone cannot explain the number of r-process stars discovered in this work within the lifetime of the universe. Current estimates of neutron-star merger rates imply that there should be about 13,000 r-process enhanced stars in the Milky Way, and about $80$ in LAMOST DR2. We find that neutron-star mergers are able to create all currently known r-process enhanced stars within $10.57 \times 10^{9}$ years. To our knowledge, this is the first work that links the rates of neutron-star mergers to the number of r-process stars in the Milky Way. All 47 r-process enhanced stars have $[{\rm Fe/H}] > -2$, providing the first evidence against the hypothesis that r-process signatures are only found in poor metallicity environments.
	\end{abstract}

@@

	\begin{figure}
		\includegraphics[width=\columnwidth]{423451}
		\caption{The spectral region around two Europium absorption lines at 4129 and 4205 Angstroms. This particular star's spectra (black) shows clear absorption at these wavelengths, as compared to the data-driven model (red).}
		\label{fig:starindex_423451}
	\end{figure}

@@

    It was found that in the Milky Way there should be present 13,194 r-process stars enhanced solely from neutron-star mergers. Taking into account that this should be considered a lower-bound estimate (by assuming a lower bound Europium abundance) this is a startlingly large difference from the known 61 r-process stars in the Milky Way.

    In preparing these calculations we assumed a constant star formation rate of 2 M$_\odot {\rm yr}^{-1}$ in the disk of the Milky Way, with a typical IMF and giant star birth rate of approximately 0.3 stars per year. Therefore if we assume a steady-state system, the number of red giant stars in the Milky Way comes to approximately $7.53\times10^7$. This allows us to find the fraction of the Milky Ways giants that our sample of r-process stars represents. Multiplying this fraction by the 13,194 stars that should be present in the Milky Way, we expect to be present 80 enhanced stars in LAMOST DR2, a number consistent with the 61 we now know of.

@@

    In an effort to confirm these numbers, we approached the calculation from a different direction. Were we to take our sample of 47 giants found in the LAMOST data, and increase it to the full estimated amount of giants in the galaxy (75,300,000), then we would expect to find 7849 enhanced giant stars, very close to the 13,194 stars from the previous calculation.

>>>>

	\begin{abstract}
		The production of heavy elements occurs through the slow and rapid neutron capture process. Numerous sites satisfy the conditions needed for the r-process but the relative frequency of these sites is unknown, largely due to the lack of a large number of stars with strong r-process signatures. Here we report the discovery of 47 r-process enhanced stars discovered in the second LAMOST data release (DR2), more than doubling the known number in the Galaxy. Taking expected rates of core-collapse supernovae and the average r-process material ejected per event, we find that core-collapse supernovae alone cannot explain the number of r-process stars discovered in this work within the lifetime of the universe. Current estimates of neutron-star merger rates imply that there should be about 13,000 r-process enhanced stars in the Milky Way, and about $79$ in LAMOST DR2. We find that neutron-star mergers are able to create all currently known r-process enhanced stars within $10.57 \times 10^{9}$ years. To our knowledge, this is the first work that links the rates of neutron-star mergers to the number of r-process stars in the Milky Way. All 47 r-process enhanced stars have $[{\rm Fe/H}] > -2$, providing the first evidence against the hypothesis that r-process signatures are only found in poor metallicity environments.
	\end{abstract}

@@

	\begin{figure}
		\includegraphics[width=\columnwidth]{229257}
		\caption{The spectral region around two Europium absorption lines at 4129 and 4205 Angstroms. This particular star's spectra (black) shows clear absorption at these wavelengths, as compared to the data-driven model (red).}
		\label{fig:starindex_229257}
	\end{figure}

@@

    It was found that in the Milky Way there should be present 13,060 r-process stars enhanced solely from neutron-star mergers. Taking into account that this should be considered a lower-bound estimate (by assuming a lower bound Europium abundance) this is a startlingly large difference from the known 61 r-process stars in the Milky Way.

    In preparing these calculations we assumed a constant star formation rate of 2 M$_\odot {\rm yr}^{-1}$ in the disk of the Milky Way, with a typical IMF and giant star birth rate of approximately 0.3 stars per year. Therefore if we assume a steady-state system, the number of red giant stars in the Milky Way comes to approximately $7.53\times10^7$. This allows us to find the fraction of the Milky Ways giants that our sample of r-process stars represents. Multiplying this fraction by the 13,060 stars that should be present in the Milky Way, we expect to be present 79 enhanced stars in LAMOST DR2, a number consistent with the 61 we now know of.

@@

    In an effort to confirm these numbers, we approached the calculation from a different direction. Were we to take our sample of 47 giants found in the LAMOST data, and increase it to the full estimated amount of giants in the galaxy (75,300,000), then we would expect to find 7849 enhanced giant stars, very close to the 13,060 stars from the previous calculation.
